%-------------------------
% Resume in LaTeX
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underline
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Kostadin Devedzhiev} \\ \vspace{5pt}
    \small \faPhone* \texttt{+44 7950 483811} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \href{mailto:kostadin.g.devedzhiev@gmail.com}{\texttt{kostadin.g.devedzhiev@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGlobe \hspace{2pt} \href{https://kostadindev.github.io/}{\texttt{kostadindev.github.io}}
    \\ \vspace{-3pt}
\end{center}

%----------SUMMARY----------
\section{SUMMARY}
\small{MPhil researcher at the University of Cambridge specialising in human--AI orchestration and multi-agent systems. Three years of industry experience building AI-driven security products at Stellar Cyber, with a track record of shipping LLM-powered features showcased at RSA and Black Hat. Research interests span interactive machine learning, active learning, human-in-the-loop frameworks, and responsible AI deployment.}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Cambridge}{Oct. 2025 -- Jun. 2026}
      {MPhil in Human-Inspired Artificial Intelligence $\cdot$ Homerton College}{Cambridge, UK}
      \resumeItemListStart
        \resumeItem{Centre for Human-Inspired AI (CHIA), TRACE Lab; supervised by Prof.\ Umang Bhatt}
      \resumeItemListEnd

    \resumeSubheading
      {Stony Brook University}{Aug. 2018 -- May 2022}
      {BS in Computer Science \& Applied Mathematics and Statistics}{Stony Brook, NY}
      \resumeItemListStart
        \resumeItem{Specialisation: AI \& Data Science $\cdot$ CS Honors Program $\cdot$ GPA 3.89\,/\,4.00 $\cdot$ Summa Cum Laude}
      \resumeItemListEnd

    \resumeSubheading
      {University of Hawai\kern.05em`\kern.05emi at Hilo}{Aug. 2019 -- May 2020}
      {National Student Exchange Program $\cdot$ Computer Science}{Hilo, HI}
      \resumeItemListStart
        \resumeItem{GPA 3.97\,/\,4.00}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Stellar Cyber}{May 2022 -- Sep. 2025}
      {Software Engineer}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{multi-agent autonomous SOC system} that triages security cases by correlating alerts with LLMs and generating analyst-ready summaries; featured as Stellar's flagship demo at \textbf{RSA 2025} and \textbf{Black Hat 2025}.}
        \resumeItem{Built the chat interface, session management, and multi-chart visualisation suite for \textbf{Open XDR Investigator}, a GenAI copilot translating natural-language prompts into Elasticsearch queries; headlined \textbf{RSA 2024} and \textbf{Black Hat 2024}.}
        \resumeItem{Implemented bidirectional WebSocket communication with parallel data and LLM requests, \textbf{cutting average response times by 70\%} and enabling real-time progress streaming.}
        \resumeItem{Developed knowledge-enriched GPT agents for log analysis, product metrics, connector normalisation, and data-source classification, each capable of visualisations, API calls, and script execution.}
        \resumeItem{Owned the product analytics framework (Mixpanel), producing reports that informed UX redesigns, storage optimisation, and behavioural segmentation.}
        \resumeItem{Maintained \textbf{>90\% test coverage} on owned components, \textbf{reducing bug filings by 34\%} year-over-year.}
      \resumeItemListEnd

    \resumeSubheading
      {Stony Brook University}{Aug. 2021 -- May 2022}
      {NLP Research Assistant}{Stony Brook, NY}
      \resumeItemListStart
        \resumeItem{Designed \textbf{Recursive QA}, a framework for generating formal-representation annotations of natural-language specifications via guided question-answering over constituency parse trees.}
        \resumeItem{Reduced redundant annotation options using affinity clustering on Levenshtein distance; achieved \textbf{>80\% inter-annotator agreement} with experienced users completing annotations in $\sim$30\,s.}
        \resumeItem{Built a full-stack annotation tool with account management, work-history tracking, and graph visualisations.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Hawai\kern.05em`\kern.05emi at Hilo}{Jun. 2020 -- Aug. 2020}
      {AI Research Assistant}{Hilo, HI}
      \resumeItemListStart
        \resumeItem{Developed an IoU\,/\,F1-based threshold estimation heuristic to optimise real-time CNN proposal acceptance for \textbf{invasive-species detection} in drone imagery.}
        \resumeItem{Enhanced a human-in-the-loop semi-automatic annotation tool that progressively increases AI assistance as model accuracy improves during training.}
      \resumeItemListEnd

    \resumeSubheading
      {University of Hawai\kern.05em`\kern.05emi at Hilo}{Mar. 2020 -- May 2020}
      {Creative Electronic Media Assistant}{Hilo, HI}
      \resumeItemListStart
        \resumeItem{Built a hologram display API and developed the Data Visualisation Lab website.}
      \resumeItemListEnd

    \resumeSubheading
      {Vivansa}{Jun. 2019 -- Aug. 2019}
      {Software Engineering Intern}{Sofia, Bulgaria}
      \resumeItemListStart
        \resumeItem{Improved CRM front-end components and resolved erroneous database entries through root-cause analysis and automated data-cleaning procedures.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{RESEARCH \& PROJECTS}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Tailor} -- \small{Human-AI Orchestration Platform}}{}
          \resumeItemListStart
            \resumeItem{Visual workflow builder for composing AI agents with human-in-the-loop review steps and governance controls, designed for regulated industries.}
            \resumeItem{Presented at the \textbf{IndiaAI Research Symposium} (Feb.\ 2026).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{MARL-Align} -- \small{Multi-Agent RL for LLM Value Alignment}}{}
          \resumeItemListStart
            \resumeItem{Multi-agent reinforcement learning framework that aligns LLM outputs using social welfare functions.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{GONEXT} -- \small{In-game GenAI Assistant for League of Legends}}{}
          \resumeItemListStart
            \resumeItem{Delivers real-time strategy recommendations by feeding live game state (allies, enemies, items, matchups) to LLMs. Released an \textbf{open-source MCP server} wrapping all Riot Games LoL APIs.}
            \resumeItem{Production-hardened with caching, rate limiting, and optimised LLM chains.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Knowledge Base Builder} -- \small{Multi-Source KB Construction with LLMs}}{}
          \resumeItemListStart
            \resumeItem{Ingests 11 source types to construct knowledge bases using LLM-powered extraction and structuring.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Threat Explorer} -- \small{Agentic Architectures for Cybersecurity}}{}
          \resumeItemListStart
            \resumeItem{Agentic system for cybersecurity investigation with a user study evaluating analyst workflows.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Fairness and Transparency Analysis} -- \small{Hospital Readmission Prediction}}{}
          \resumeItemListStart
            \resumeItem{Analysed fairness in hospital readmission models; achieved \textbf{74.5\% disparity reduction} through bias-mitigation techniques.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Symbiotic Learning} -- \small{Human-in-the-Loop Image Annotation}}{}
          \resumeItemListStart
            \resumeItem{Semi-automatic annotation tool for ecological conservation that progressively increases AI assistance as model accuracy improves.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{I Want to Redistrict} -- \small{Senior Software Engineering Capstone}}{}
          \resumeItemListStart
            \resumeItem{Processed 2020 US Census data on a supercomputer to generate viable state districting plans via stochastic graph algorithms, optimising for political fairness and compactness.}
            \resumeItem{Built a web application for visual and statistical analysis of equitable districting results.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Deep Gestures} -- \small{Gesture Recognition on Arduino Nano 33}}{}
          \resumeItemListStart
            \resumeItem{Trained and deployed a gesture recognition model on an Arduino Nano 33 BLE microcontroller.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PUBLICATION-----------
\section{PUBLICATION}
\resumeSubHeadingListStart
  \item\small{P-M Binder, \textbf{K.\,G.\,Devedzhiev}, A.\,T.\,Runyan. \textit{Motional emf generated by squeezing an elliptical conducting loop.} European Journal of Physics, 2020. \href{https://doi.org/10.1088/1361-6404/ABB066}{\myuline{doi:10.1088/1361-6404/ABB066}}}
\resumeSubHeadingListEnd

%-----------TEACHING & MENTORSHIP-----------
\section{TEACHING \& MENTORSHIP}
\resumeSubHeadingListStart
  \item\small{\textbf{AI Leadership Mentor}, UniHawk (Kuwait City, Dec.\ 2025) -- Mentored high-school students through a week-long AI app-building bootcamp.}
  \item\small{\textbf{Teaching Assistant}, Stony Brook University (Aug.\ 2020 -- May 2021) -- AMS 210: Applied Linear Algebra; held weekly office hours and graded coursework.}
  \item\small{\textbf{Grader}, University of Hawai\kern.05em`\kern.05emi at Hilo (Oct.\ 2019 -- May 2020) -- MATH 311: Linear Algebra; CS 150: Intro to Computer Science.}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
\resumeSubHeadingListStart
  \item\small{\textbf{IBM Generative AI Engineering} -- IBM}
  \item\small{\textbf{MCP: Build Rich-Context AI Apps with Anthropic} -- Anthropic}
  \item\small{\textbf{AI Agents in LangGraph} -- DeepLearning.AI}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Domains}{: Full-Stack Development, Machine Learning, NLP, Human-Computer Interaction, Data Science}\vspace{2pt} \\
     \textbf{Languages}{: Python, JavaScript, TypeScript, C}\vspace{2pt} \\
     \textbf{Frontend}{: React, Angular, Tailwind}\vspace{2pt} \\
     \textbf{Backend \& APIs}{: FastAPI, NodeJS, Express, Flask}\vspace{2pt} \\
     \textbf{Databases}{: MongoDB, Elasticsearch, Pinecone, PostgreSQL, Redis}\vspace{2pt} \\
     \textbf{Data Science \& ML}{: PyTorch, Hugging Face, Pandas, NumPy, Scikit-learn, Plotly}\vspace{2pt} \\
     \textbf{AI Frameworks}{: LangChain, LangGraph}\vspace{2pt} \\
     \textbf{DevOps}{: Docker}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
